\documentclass{article}
\begin{document}
		\title{\underline{\textbf{BRIEF HISTORY OF PYTHON}}}
		\maketitle
		\begin{itemize}
			\item Python was conceived in the late 1980s by \emph{Guido Van Rossum} at Centrum Wiskunde and Informatica as a successor to ABC programming language. It was first released by Van Rossum on Feb 20th, 1991.Van Rossum shouldered the sole responsibility for the project as, the lead developer, until 12 july, 2018.
			\item Python 2.0 was released on 16 OCT 2000, with many major new features,including a cycle-dictating garbage collector and support for Unicode
			\item Python 3.0 was released on 3 DEC 2008.
			\item Python 3.9.2 and 3.9.8 were expedited as all versions of Python had security issues, leading to possible remote code execution and web cache poisoning.
			\\ \textbf{FROM CITATION BOT, WIKIPEDIA}
			\section{MORE ABOUT THE FOUNDER}
			One of the amazing facts about python is the fact that it belongs to solely one person.
			\\ Normally, there is a bit of a controversy regarding the original developer of most programming languages. This is not the case in python as the original founder is wel-known.
			\\Credit is also reserved for the tireless and yet anonymous programmers,testers and users which contribute to the speed with which python has spread around the world.
			\item Some similar or related programming languages to python include:\emph{Java, R language, JavaScript, Scala and Amaconda.}
			\item Some available Integrated development environment for Python include: \emph{Pycharm, Kite, Spyder, Sublime text 3, Visual Studio code, Atom, Pydew e.t.c}
			\section{Some applications that can be developed from python include:}
			\item Instagram
			\item Pinterest
			\item Spotify
			\item Uber
			\item Dropbox
		\end{itemize}
		\end{document}