\documentclass{article}
\begin{document}
	\title{\underline{\textbf{JAVA}}}
	\maketitle
	\section{WHY JAVA?}
	Java is a simple and efficient general-purpose language that is primarily used for Internet-based applications
	\section{WHAT IS JAVA?}
	Java is a high-level, class-based, object-oriented programming language that is designed to have a few implementation dependencies as possible. It is a general-purpose programming language intended to let programmers write once, run anywhere (WORA). This means that compiled Java code can run on all platforms that support Java without the need for recompilation. 
	\section{BRIEF HISTORY ON JAVA}
	\textbf{Java was originally developed by James Gosling at Sun microsystems(which has since been acquired by oracle) and released in 1995 as a core component of Sun Microsystems’ Java platform.}
	\paragraph{James Gosling, Mike Sheridan and Patrick Naughton initiated the Java language project in June 1991. Sun microsystems released the first public implementation as Java 1.0 in 1996. It promised WORA functionality with the advent of Java 2 (released initially as J2SE 1.2 in December (1998-1999), new versions had multiple configurations built for different types of platforms.}
	\paragraph{In 1997, sun microsystems approached the ISO/IEC JTC 1 standards body and later the ECMA international to formalize java, but it soon withdrew from the process.}
	\paragraph{In January 2016, Oracle announced that Java run-time environments based on JDK 9 will discontinue the browser plugin. Java software runs on everything from laptops to data centers, game consoles to scientific supercomputers. (FROM: Wikipedia; Jochem Van Hees)}
	
\end{document}